### 2014-08-31 fundamentals/intro.tex
bold words

Myriad challenges in nuclear fuel cycle analysis could be 
addressed with an agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions.

@@

The \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios. \Cyclus is a dynamic 
simulator that treats both materials and facilities discretely, with an 
architecture that permits simulations with multiple and variable levels of 
fidelity.

>>>>

The fundamental concepts of the \Cyclus nuclear fuel cycle simulator capture 
these modern insights so that challenges in nuclear fuel cycle analysis can be 
better addressed.

@@

The \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

\Cyclus is a dynamic simulator that treats both materials and facilities discretely, with an 
architecture that permits simulations with multiple and variable levels of 
fidelity. Its agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing field of fuel cycle simulators.
